\chapter{Introduction}

\par

The collection and analysis of biometric data play a significant role in understanding the relationship between physical fitness and gaming performance. This research aims to investigate
how various physical parameters, such as HRV (Heart Rate Variability), Heart Rate Max, Heart Reate average, Active Sleep and Quality of Sleep, influence a user's performance in a digital game, in this case
PUBG: Battlegrounds. The research will also explore the potential of using biometric data to suggest the most suitable settings for different game scenarios. By using wearable technology, which can monitor metrics such as
heart rate, sleep, and activity, this study seeks to establish a correlation between the player's physical condition and their performance in a digital game scenario. 

The importance of fitness data in this context cannot be overstated. Heart Rate Variability (HRV), maximum heart rate, active sleep, and sleep quality are all essential indicators of a person's physical condition.
THese metrics offers a comprehensive insight into the user's physical condition, which can be used to improve their gaming performance. 

\textbf{Heart Rate Variability (HRV):} is a measure of the variation in time between each heartbeat, and it is closely linked to the body's stress levels. HRV is widely used as a measure
of the body's autonomic nervous system, which controls the body's stress response. A higher HRV is associated with a lower stress level, while a lower HRV is associated with a higher stress level. 
A research from E. Ortega\cite{ortega2018pre} highlights the importance of HRV in sports science, as a way of understanding the psychological state of atheletes before competions. It found
a positive correlation between HRV, self-efficacy, and performance among sport shooters. Advanced shooters demonstrated lower average heart rates and employed mental skills more effectively than less experienced shooters.
This suggests HRV as a valuable asset, when tranferring the psychological state of the athlete to the performance in a digital game. It allows for a better understanding of the player's stress levels, and how it affects their performance.
This personalized approach can enhance player experience, and potentially improve their performance in the game. 
\par
The Heart Rate Variability measurements typically requires a chest strap, and measurements typically span from 5 minutes to 24 hours, it is commonly used in clinical settings to evaluate 
cardiac conditions.\cite{malik1996heart} Short-term HRV analysis lasting less then 5 minutes have been proven to provide more accurate estimations compared to longer measurements.\cite{mcnames2006reliability}
Based on this, the research will focus on short-term HRV measurements, as it is more practical for the user, and it provides accurate estimations. It will be more detailed in the methodology section.

\textbf{Heart Rate Max:} is the maximum number of times the heart can beat in a minute, and it is a measure of the body's cardiovascular fitness. It is an important indicator of the body's physical condition, and it is used to 
evaluate the body's ability to perform physical activities, reflecting their cardiovascular fitness. In this research, understanding HRmax is vital for assessing participants fitness and endurance.
It could indicates how well players can handle stress and maintain their concentration over extended periods of time. By analysing alongside other biometric data this research could
uncover valuable insight into optmizing players performance in a digital game scenario.

\textbf{Heart Rate Average:} is the average number of times the heart beats in a minute, and it is a measure of the body's physical activity. It is also an important indicator of the body's physical condition, 
and it is another measure of the body's cardiovascular fitness. It is used to evaluate the body's ability to perform physical activities, reflecting their cardiovascular fitness.

\textbf{Active Step:} Active steps, as a mesure of physical activity, is an important indicator of the body's physical condition. It is used to evaluate the body's ability to perform
physical activities, reflecting their cardiovascular fitness. Counting the numbers of steps taken daily can help track overall physical activity, and it is a good indicator of the body
physical condition. It is also used to evaluate the body's ability to perform physical activities, reflecting their cardiovascular fitness.
 

\textbf{Quality of Sleep:} are important indicators of the body's recovery and readiness for physical activity. Active sleep is a measure of the body's physical activity during sleep, 
and it is an important indicator of the body's recovery and readiness for physical activity. High-quality sleep, marked by sufficient duration and minimal disruptions, is fundamental for 
overall health impacting mood, cognitive fucntion.  A research that evaluated Sleep and performance in Eathletes \cite{BONNAR2019647} uderscores the critical role of sleep in Eathletes performance in Esports, 
showing its impact on cognitive functions as a crucial factor for competitives success. Adequate sleep improves information processing, visual motor functioning, attention, working memory, and other functions 
essential for decision-making and reaction time. On the other hand, sleep depravation can significantly impair these cognitive abilities, potentially to poor performance. For this research it
proves the importance of sleep in the context of gaming performance, and how it can be used to predict the player's readiness and tune their performance in a digital game scenario.









