\chapter{Machine Learning Models}

\section{Introduction}
As explained in dept in the methodology chapter, the biometric data collected through the watches generated a total of 6 independent variables:



\begin{itemize}
    \item Heart Rate Maximum \textit{bm\_HR\_max}
    \item Heart Rate Average \textit{bm\_HR\_avg}
    \item Heart Rate Variability \textit{bm\_HR\_var}
    \item Activity Steps \textit{bm\_act\_steps}
    \item Sleep \textit{bm\_sleep}
\end{itemize}

The dependent variables that were collected through the gaming tests are:

\begin{itemize}
    \item Fine Motor Average Tracking Time \textit{fm\_avg\_trk\_time}
    \item Fine Motor Accuracy \textit{fm\_accuracy}
    \item Visual Average Response Time \textit{vx\_avg\_res\_time}
    \item Visual Shot Accuracy \textit{vx\_shot\_accuracy}
    \item Visual Target Accuracy \textit{vx\_trg\_accuracy}
    \item Audio Average Response Time \textit{au\_avg\_res\_time}
\end{itemize}

The goal based on the research question was to find the correlation between the independent and dependent variables. When approaching a machine learning problem, one of the fundamental
considerations is whether the problem is a regression or classification problem.

\subsection*{Classification vs Regression Problem}
The main difference between a classification and regression problem is the type of dependent variable. The dependent variable, can be one or more, and they are the variables that are being predicted. In
classification, the dependent variable is categorical, meaning it can take one of a limited number of values. Examples includes predicting whether an email is spam or not,
predicting whether a patient has a disease or not. In regression, the dependent variable is continuous and numerical, meaning it can take any value within a range. Examples
includes predicting house prices, stock prices, temperature. In this project, the dependent variables are continuous and numerical, making it a regression problem. The goal
was to predict the dependent variables based on the biometric data collected from the watches.




